---
title: "PLSC 30600 --- Take-Home Midterm: LaLonde (1986) and Nonexperimental ATT"
output:
  pdf_document:
    number_sections: false
header-includes:
  - "\\usepackage[margin=1in]{geometry}"
  - "\\usepackage{amsmath, amssymb, amsthm}"
  - "\\usepackage{bm}"
  - "\\usepackage{booktabs}"
  - "\\usepackage{enumitem}"
  - "\\usepackage{hyperref}"
  - "\\usepackage{tikz}"
  - "\\usetikzlibrary{positioning}"
  - "\\setlist[itemize]{noitemsep, topsep=2pt}"
  - "\\setlist[enumerate]{itemsep=4pt, topsep=6pt}"
  - "\\newcommand{\\E}{\\textrm{E}}"
  - "\\newcommand{\\Y}{\\bm{Y}}"
  - "\\newcommand{\\D}{\\bm{D}}"
  - "\\newcommand{\\one}{\\bm{\\mathbf{1}}}"
  - "\\newcommand{\\X}{\\bm{X}}"
  - "\\newcommand{\\W}{\\bm{W}}"
---

\textbf{Due:} Friday, February 13 (11:59pm)

\vspace{0.75em}
\hrule
\vspace{0.75em}


NB: This code sample is a subsection of a take home midterm completed for my graduate level class at the University of Chicago, PLSC 30600: Causal Inference. 


```{r setup, include=FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE
)
```

# Overview

In the last homework you used the experimental NSW data to estimate the
ATE. In this take-home midterm you will use nonexperimental data to
estimate the ATT. You will work with the Dehejia–Wahba (1999) subset of the 
experimental sample, as well as observational control data, and will then 
evaluate estimators.

Reference tutorial: https://yiqingxu.org/tutorials/lalonde/

We follow many of the procedures used in the tutorial, but they have some built
in functions and use some machine learning estimators that we haven't covered; we 
are going to put together the pieces using different estimation techniques. 
You are allowed to use the tutorial for reference, for understanding the data 
and context, but their code will not carry over directly. 

# Data and setup

In our analysis, as in the tutorial, will use three samples built around the
LaLonde–Dehejia–Wahba (LDW) data: (1) LDW-Experimental, which is the
experimental subset of the original experimental data; (2) LDW-CPS1, which pairs 
the LDW-Experimental treated units with observational controls from the Current 
Population Survey (CPS-SSA-1) ; and (3) LDW-PSID1, which pairs the same LDW 
treated units with observational controls from the Panel Study of Income 
Dynamics (PSID-1).

`ldw_cps` and `ldw_psid` already *include* the LDW treated observations. 
The experimental control group is stored separately as
`ldw_co`.

```{r}
library(Matching)
library(estimatr)

# Load prepared objects (nsw, ldw, ldw_cps, ldw_psid, ldw_co, etc.)
lalonde_url <- "https://raw.githubusercontent.com/xuyiqing/lalonde/master/data/lalonde.RData"
load(url(lalonde_url))

# define variables
Y <- "re78"
treat <- "treat"
covar <- c("age", "education", "black", "hispanic", "married", "nodegree",
           "re74", "re75", "u74", "u75")
```


# Problems

## Part 1: Constructing the Comparison Samples

### 1.1 Re-estimate propensity scores (LDW-Experimental, CPS1, PSID1)

Estimate the treatment propensity score for each of these datasets:
LDW-Experimental (`ldw`), LDW-CPS1 (`ldw_cps`), and LDW-PSID1
(`ldw_psid`). Use a logit model with `glm(..., family = binomial())` and
the covariate set `covar`.

Create and use the following object names:

- `exp_df` for LDW‑Experimental
- `cps_untrim` for LDW‑CPS1 (untrimmed)
- `psid_untrim` for LDW‑PSID1 (untrimmed)

```{r}
exp_df <- ldw
cps_untrim <- ldw_cps
psid_untrim <- ldw_psid
```

Deliverable: redefined datasets, no results reporting needed for this problem. 

## Answer

```{r}
exp_df <- ldw
cps_untrim <- ldw_cps
psid_untrim <- ldw_psid
```

```{r warning=FALSE}
#Estimate propensity scores for each dataset
glm_exp_df <- glm(treat ~ age + education + black + hispanic + married + 
                    nodegree + re74 + re75 + u74 + u75, data = exp_df, 
                  family = binomial(link = "logit"))
exp_df$p_hat <- predict(glm_exp_df, type = "response")

glm_cps_untrim <- glm(treat ~ age + education + black + hispanic + married + 
                        nodegree + re74 + re75 + u74 + u75, data = cps_untrim, 
                      family = binomial(link = "logit"))
cps_untrim$p_hat <- predict(glm_cps_untrim, type = "response")

glm_psid_untrim <- glm(treat ~ age + education + black + hispanic + married + 
                         nodegree + re74 + re75 + u74 + u75, data = psid_untrim,
                       family = binomial(link = "logit"))
psid_untrim$p_hat <- predict(glm_psid_untrim, type = "response")
```

### 1.2 Propensity score overlap plots

Using `ggplot2` and `geom_histogram`, plot propensity score overlap for
each merged dataset and for the true experimental population. Use
different fill colors for treated vs control and label each plot clearly
(LDW-CPS1 vs LDW-PSID1 vs LDW-Experimental).
Use `aes(y = after_stat(density))` so the y-axis is density rather
than counts.
Also report the number of treated and control observations for each
dataset you plot. 

Deliverable: three overlap plots each accompanied by treated/control counts. 

## Answer

```{r warning=FALSE}
library(ggplot2)

# Plot distribution of propensity scores

ggplot(exp_df, aes(x = p_hat, fill = factor(treat))) +
  geom_histogram(aes(y = after_stat(density)),
                 position = "identity", alpha = 0.5, bins = 30) +
  scale_fill_manual(values = c("#E69F00", "#56B4E9")) +
  labs(x = "Propensity score", y = "Density", fill = "Group", title = "EXP_DF") +
  theme_minimal()

ggplot(cps_untrim, aes(x = p_hat, fill = factor(treat))) +
  geom_histogram(aes(y = after_stat(density)),
                 position = "identity", alpha = 0.5, bins = 30) +
  scale_fill_manual(values = c("#E69F00", "#56B4E9")) +
  labs(x = "Propensity score", y = "Density", title = "CPS_UNTRIM", fill = "Group") +
  theme_minimal()

ggplot(psid_untrim, aes(x = p_hat, fill = factor(treat))) +
  geom_histogram(aes(y = after_stat(density)),
                 position = "identity", alpha = 0.5, bins = 30) +
  scale_fill_manual(values = c("#E69F00", "#56B4E9")) +
  labs(x = "Propensity score", y = "Density", title = "PSID_UNTRIM", fill = "Group") +
  theme_minimal()

# Print counts for treatment and control for each dataset
cat("exp_df treatment: ", sum(exp_df$treat == 1), "\n")
cat("exp_df control: ", sum(exp_df$treat == 0), "\n")
cat("cps_untrim treatment: ", sum(cps_untrim$treat == 1), "\n")
cat("cps_untrim control: ", sum(cps_untrim$treat == 0), "\n")
cat("psid_untrim treatment: ", sum(psid_untrim$treat == 1), "\n")
cat("psid_untrim control: ", sum(psid_untrim$treat == 0), "\n")
```


### 1.3 Add experimental controls + re-estimate + trim

For each of the two combined datasets, create a new data set that merges in the 
experimental controls from `ldw_co` to expand the control group. Then, on these 
new expanded data sets, estimate each unit’s propensity **of being included in 
the experiment** using `covar`.

We are going to use this experimental propensity score to implement trimming. 
On these new data sets, drop units with extreme propensity scores as follows:
- LDW-CPS1: drop units with propensity score > 0.9
- LDW-PSID1: drop units with propensity score > 0.8

Create and use these object names:

- `ldw_cps.plus` and `ldw_psid.plus` for the expanded datasets
- `ldw_cps.plus_trim` and `ldw_psid.plus_trim` after trimming
- `cps_trim` and `psid_trim` for ATT analysis (samples 1&3, 1&4)

Deliverable: redefined datasets, no results reporting needed for this problem. 

**Note:** Before `rbind`, make sure the two data frames have
the same columns and create a new indicator (e.g., `experimental`) for
the experiment status. Then estimate `experimental ~ covar` by logit and
trim on that fitted probability.

## Answer

```{r warning=FALSE}
# Create a p_hat column for ldw_co so that all the columns are the same before merging
ldw_co$p_hat <- NA

# Create experimental indicator for all data sets. 1 = experimental, 0 = non-experimental 

ldw_co$experimental <- 1

# treatment is experimental, control is non-experimental 
cps_untrim$experimental <- ifelse(cps_untrim$treat == 1, 1, 0)
psid_untrim$experimental <- ifelse(psid_untrim$treat == 1, 1, 0)
```


```{r warning=FALSE}
library(dplyr)

# Combine ldw_co and cps_untrim
ldw_cps.plus <- rbind(cps_untrim, ldw_co)

# Combine ldw_co and psid_untrim 
ldw_psid.plus <- rbind(psid_untrim, ldw_co)

# use glm (experimental ~ covar) on both combined datasets
glm_ldw_cps.plus <- glm(experimental ~ age + education + black + hispanic + 
                          married + nodegree + re74 + re75 + u74 + u75, 
                        data = ldw_cps.plus, family = binomial(link = "logit"))
ldw_cps.plus$p_exp <- predict(glm_ldw_cps.plus, type = "response")

glm_ldw_psid.plus <- glm(experimental ~ age + education + black + hispanic +
                          married + nodegree + re74 + re75 + u74 + u75, 
                         data = ldw_psid.plus, family = binomial(link = "logit"))
ldw_psid.plus$p_exp <- predict(glm_ldw_psid.plus, type = "response")

# Use experiment propensity scores to trim 

ldw_cps.plus_trim <- ldw_cps.plus[ldw_cps.plus$p_exp <= 0.9, ]
ldw_psid.plus_trim <- ldw_psid.plus[ldw_psid.plus$p_exp <= 0.8, ]

# Data sets for ATT analysis

# if experimental and control, drop
cps_trim <- ldw_cps.plus_trim %>%
            filter(!(ldw_cps.plus_trim$treat == 0 & ldw_cps.plus_trim$experimental == 1))

psid_trim <- ldw_psid.plus_trim %>%
            filter(!(ldw_psid.plus_trim$treat == 0 & ldw_psid.plus_trim$experimental == 1))
```


### 1.4 Propensity score matching (1:1)

Using the trimmed datasets from Problem 1.3, perform 1:1 nearest-neighbor
propensity score matching **without replacement**. Steps:

1) Keep only treated LDW units and nonexperimental controls:
   - CPS: `sample %in% c(1, 3)`
   - PSID: `sample %in% c(1, 4)`
2) Re-estimate the propensity score (logit `glm`) on the filtered sample.
3) Match treated to controls on the propensity score with
   `Matching::Match`, using `M = 1`, `replace = FALSE`, `ties = FALSE`,
   and `estimand = "ATT"`. The key arguments are:
   - `Y`: outcome (`re78`)
   - `Tr`: treatment indicator (`treat`)
   - `X`: the propensity score vector
4) Extract the matched rows using `index.treated` and `index.control`,
   then bind those rows to form a matched dataset for later steps.

Create and use:
- `ldw_cps_matched` and `ldw_psid_matched`

**Note:** `Matching::Match` returns indices. You can recover
the matched data with something like
`matched_df <- rbind(df[m$index.treated, ], df[m$index.control, ])`.


## Answer

```{r warning=FALSE}
# Re-estimate treatment propensity scores

glm_cps_trim <- glm(treat ~ age + education + black + hispanic + married + 
                      nodegree + re74 + re75 + u74 + u75, data = cps_trim, 
                    family = binomial(link = "logit"))
cps_trim$p_hat2 <- predict(glm_cps_trim, type = "response")

glm_psid_trim <- glm(treat ~ age + education + black + hispanic + married + 
                       nodegree + re74 + re75 + u74 + u75, data = psid_trim, 
                     family = binomial(link = "logit"))
psid_trim$p_hat2 <- predict(glm_psid_trim, type = "response")

# Match treated to controls

m_cps <- Match(Y = cps_trim$re78, Tr = cps_trim$treat, X = cps_trim$p_hat2, 
               M = 1, replace = FALSE, ties = FALSE, estimand = "ATT")

m_psid <- Match(Y = psid_trim$re78, Tr = psid_trim$treat, X = psid_trim$p_hat2, 
                M = 1, replace = FALSE, ties = FALSE, estimand = "ATT")

# Create matched datasets

ldw_cps_matched <- rbind(cps_trim[m_cps$index.treated, ], cps_trim[m_cps$index.control, ])

ldw_psid_matched <- rbind(psid_trim[m_psid$index.treated, ], psid_trim[m_psid$index.control, ])


```

### 1.5 Re-assess overlap after matching

Plot propensity score overlap for the matched CPS and PSID datasets.
Use `ggplot2` and `geom_histogram` with `aes(y = after_stat(density))`.
Report the number of treated and control observations for each matched
dataset.

Deliverable: two overlap plots each accompanied by treated/control counts

# Answer

```{r warning=FALSE}
# Plot new propensity score distributions 
ggplot(ldw_cps_matched, aes(x = p_hat2, fill = factor(treat))) +
  geom_histogram(aes(y = after_stat(density)),
                 position = "identity", alpha = 0.5, bins = 30) +
  scale_fill_manual(values = c("#E69F00", "#56B4E9")) +
  labs(x = "Propensity score", y = "Density", title = "LDW_CPS_MATCHED", fill = "Group") +
  theme_minimal()

ggplot(ldw_psid_matched, aes(x = p_hat2, fill = factor(treat))) +
  geom_histogram(aes(y = after_stat(density)),
                 position = "identity", alpha = 0.5, bins = 30) +
  scale_fill_manual(values = c("#E69F00", "#56B4E9")) +
  labs(x = "Propensity score", y = "Density", title = "LDW_PSID_MATCHED", fill = "Group") +
  theme_minimal()

# Print treatment and control counts for both datasets 
cat("ldw_cps_matched treatment: ", sum(ldw_cps_matched$treat == 1), "\n")
cat("ldw_cps_matched control: ", sum(ldw_cps_matched$treat == 0), "\n")
cat("ldw_psid_matched treatment: ", sum(ldw_psid_matched$treat == 1), "\n")
cat("ldw_psid_matched control: ", sum(ldw_psid_matched$treat == 0), "\n")
```

### 1.6 Covariate balance (by hand)

Check covariate balance. For each covariate
in `covar`, compute standardized mean differences (treated - control)
pre‑matching and post‑matching. Use the original LDW‑CPS1 / LDW‑PSID1
samples for pre‑matching and the matched datasets for post‑matching.

For each dataset (CPS and PSID), make one plot where:
- x‑axis = standardized mean difference (SMD)
- y‑axis = covariate name
- show matched vs unmatched SMDs in different colors on the same plot

Comment on what you see.

Deliverable: two balance plots + a brief interpretation.

**Note:** A simple SMD for covariate `x` is
`(mean(x_t) - mean(x_c)) / sd(x_all)`, where `x_t` and `x_c` are treated
and control values and `x_all` is the pooled sample. You can wrap this in
a small function and apply it across `covar`.

## Answer

```{r warning=FALSE}
# Function that calculates standardized mean difference between treated 
#and control groups for one covariate of the data set
smd <- function(x, df) {
  x_t <- df[[x]][df$treat == 1]
  x_c <- df[[x]][df$treat == 0]
  x_all <- df[[x]]
  return((mean(x_t) - mean(x_c)) / sd(x_all))
}

# Create vectors with SMD values for each dataset, matched and unmatched
smd_cps <- numeric(0)
smd_psid <- numeric(0)
smd_cps_matched <- numeric(0)
smd_psid_matched <- numeric(0)

for (x in covar) {
    smd_cps <- c(smd_cps, smd(x, cps_untrim))
}

for (x in covar) {
    smd_psid <- c(smd_psid, smd(x, psid_untrim))
}

for (x in covar) {
    smd_cps_matched <- c(smd_cps_matched, smd(x, ldw_cps_matched))
}

for (x in covar) {
    smd_psid_matched <- c(smd_psid_matched, smd(x, ldw_psid_matched))
}

# Create dataframes, one for each dataset, that contain SMD values for 
#both matched and unmatched versions
bal_cps <- data.frame (
  covariate = rep(covar, 2),
  SMD = c(smd_cps, smd_cps_matched),
  sample = rep(c("Unmatched", "Matched"), each = length(covar))
)
bal_psid <- data.frame (
  covariate = rep(covar, 2),
  SMD = c(smd_psid, smd_psid_matched),
  sample = rep(c("Unmatched", "Matched"), each = length(covar))
)

```

```{r warning=FALSE}
# Create Balance Plots

ggplot(bal_cps,
       aes(x = SMD,
           y = covariate,
           color = sample)) +
  geom_point(size = 3) +
  geom_vline(xintercept = c(-0.1, 0.1),
             linetype = "dashed",
             color = "gray50") +
  labs(x = "Standardized Mean Difference",
       y = "Covariate",
       color = "Sample", title = "CPS") +
  theme_minimal()

ggplot(bal_psid,
       aes(x = SMD,
           y = covariate,
           color = sample)) +
  geom_point(size = 3) +
  geom_vline(xintercept = c(-0.1, 0.1),
             linetype = "dashed",
             color = "gray50") +
  labs(x = "Standardized Mean Difference",
       y = "Covariate",
       color = "Sample", title = "PSID") +
  theme_minimal()
```


### Interpretation

The matched data sets have small standardized mean differences for all covariates, while the unmatched data sets have larger absolute differences. This demonstrates that matching by propensity score has made the covariate profiles for treatment and control similar, hence the small mean difference between them. The success of the matching is also demonstrated in how the matched values are mostly within the threshold around zero. Interestingly, both data sets without matching have small mean differences between treatment and control for the hispanic covariate. 

## Part 2: ATT Estimation

Estimate the ATT using the five samples you created in Part 1:
`exp_df`, `cps_untrim`, `psid_untrim`, `cps_trim`, and `psid_trim`.

For each sample, compute the following estimators:

- difference in means, 
- Lin (`estimatr::lm_lin`), 
- IPW, 
- stabilized IPW, and
- doubly robust. 

Use bootstrap confidence intervals for all estimates and
report a single table with estimates and 95% CIs. 
Stratify bootstraps so that each bootstrap sample has the same number of treated 
and control units as the original sample 
(i.e., resample treated and control units separately).
Use at least 500 bootstrap replications.
Re-estimate the propensity scores on each bootstrap. 

Deliverable: one table with estimates + bootstrap 95% CIs.
Optional: plot estimates. 

# Answer

```{r warning=FALSE}
# Data cleaning
# Match column names for all data sets

cps_trim <- cps_trim %>% rename (
  p_old = p_hat,
  p_hat = p_hat2
)

psid_trim <- psid_trim %>% rename (
  p_old = p_hat,
  p_hat = p_hat2
)

ldw_cps_matched <- ldw_cps_matched %>% rename (
  p_old = p_hat,
  p_hat = p_hat2
)

ldw_psid_matched <- ldw_psid_matched %>% rename (
  p_old = p_hat,
  p_hat = p_hat2
)
```


```{r warning=FALSE}
# Function to calculate all estimates, complete bootstraps, and calculate 
#confidence intervals for one data set. Returns a data frame with calculated values. 

set.seed(30600)

estimate <- function(df) {
  estimators <- data.frame(
    dim = NA,
    dim_025 = NA,
    dim_975 = NA,
    lin = NA,
    lin_025 = NA,
    lin_975 = NA,
    ipw = NA,
    ipw_025 = NA,
    ipw_975 = NA,
    s_ipw = NA,
    s_ipw_025 = NA,
    s_ipw_975 = NA,
    dr = NA,
    dr_025 = NA,
    dr_975 = NA
  )
  
  #Difference in Means
  
      # Y(0) cannot be observed. The control group mean is used as a plug in.
  estimators$dim <- mean(df[[Y]][df$treat == 1]) - mean(df[[Y]][df$treat == 0])
  
  # Lin

   estimators$lin <- tryCatch({
    lm_lin(re78 ~ treat, covariates = ~ age + education + black + 
           hispanic + married + nodegree + re74 + re75 + u74 + u75, data = df)$coefficients["treat"]
  }, error = function(e) NA)
  
  # IPW
  
  w_att <- ifelse(df$treat == 1, 1, df$p_hat / (1 - df$p_hat))
  estimators$ipw <- mean(df[[Y]][df$treat == 1]) -
            sum(w_att[df$treat == 0] * df[[Y]][df$treat == 0]) / length(df[[Y]])
   
  # Stabilized IPW

  w_s_att <- ifelse(df$treat == 1, 1, (mean(df$treat) / 
                (1 - mean(df$treat))) *  (df$p_hat / (1 - df$p_hat)))
  estimators$s_ipw <- mean(df[[Y]][df$treat == 1]) -
                weighted.mean(df[[Y]][df$treat == 0] , w_s_att[df$treat == 0])
    
  # Doubly Robust

  fit_dr <- lm(re78 ~ treat + age + education + black + hispanic + married + 
                 nodegree + re74 + re75 + u74 + u75, data = df)
  df$m1_hat <- predict(fit_dr, newdata = transform(df, treat = 1))
  df$m0_hat <- predict(fit_dr, newdata = transform(df, treat = 0))
  estimators$dr <- (1 / sum(df$treat)) * sum(df$treat * (df$m1_hat - df$m0_hat) + 
                    df$treat * (df[[Y]] - df$m1_hat) -  
                (1 - df$treat) * (df$p_hat / (1 - df$p_hat)) * (df[[Y]] - df$m0_hat))
  
  # Bootstrap and CI
 
  bootstrap <- function(data, B = 500) {
    n_t <- sum(data$treat == 1)
    n_c <- sum(data$treat == 0)

    results <- replicate(B, {
        #Sample treated and control units separately 
        if (n_t != 0) {
          i <- which(data$treat == 1)
          i_t <- sample(i, replace = TRUE)
          d_t <- data[i_t, ]
        }
        if (n_c != 0) {
          i <- which(data$treat == 0)
          i_c <- sample(i, replace = TRUE)
          d_c <- data[i_c, ]
        }
        d <- rbind(d_t, d_c)
    
        # Y(0) cannot be observed. The control group mean is used as a plug in.
        dim <- mean(d[[Y]][d$treat == 1]) - mean(d[[Y]][d$treat == 0])
        
        # Lin estimator
        lin <- tryCatch({
        unname(lm_lin(re78 ~ treat, covariates = ~ age + education + black + 
           hispanic + married + nodegree + re74 + re75 + u74 + u75, data = d)$coefficients["treat"])
          }, error = function(e) NA)
        
        #re-estimate propensity scores
        glm_d <- glm(treat ~ age + education + black + hispanic + married + 
                   nodegree + re74 + re75 + u74 + u75, data = d, family = binomial(link = "logit"))
        d$p_hat <- predict(glm_d, type = "response")
    
        #IPW estimator
        w_att <- ifelse(d$treat == 1, 1, d$p_hat / (1 - d$p_hat))
        att_ipw <- mean(d[[Y]][d$treat == 1]) -
            sum(w_att[d$treat == 0] * d[[Y]][d$treat == 0]) / length(d[[Y]])
    
        #Stabilized IPW estimator
        w_s_att <- ifelse(d$treat == 1, 1, (mean(d$treat) / 
                                          (1 - mean(d$treat))) *  (d$p_hat / (1 - d$p_hat)))
        s_ipw_ate <- mean(d[[Y]][d$treat == 1]) - 
                  weighted.mean(d[[Y]][d$treat == 0] , w_s_att[d$treat == 0])
        
        #Doubly Robust Estimator
        fit_dr <- lm(re78 ~ treat + age + education + black + hispanic + married + 
                  nodegree + re74 + re75 + u74 + u75, data = d)
        d$m1_hat <- predict(fit_dr, newdata = transform(d, treat = 1))
        d$m0_hat <- predict(fit_dr, newdata = transform(d, treat = 0))
        dr_att <- (1 / sum(d$treat)) * sum(d$treat * (d$m1_hat - d$m0_hat) + d$treat *
          (d[[Y]] - d$m1_hat) -  (1 - d$treat) * (d$p_hat / (1 - d$p_hat)) * (d[[Y]] - d$m0_hat))
  
        c(dim = dim, lin = lin, ipw = att_ipw, s_ipw = s_ipw_ate, dr = dr_att)
    })
    as.data.frame(t(results))
  }

  boot <- bootstrap(df, B = 500)
  
  # Calculate confidence intervals for all estimates of the bootstrap
  ci <- apply(boot, 2, quantile, probs = c(0.025, 0.975), na.rm = TRUE)
  
  #Save CI results to estimators data frame to return
  for (name in colnames(boot)) {
   estimators[[paste0(name, "_025")]] <- ci[1, name]
   estimators[[paste0(name, "_975")]] <- ci[2, name]
  }
  
  return(estimators)
}
```

```{r}
# Calculate all estimates for all data sets and create data frame

df <- rbind(estimate(exp_df), estimate(cps_untrim), estimate(psid_untrim), 
            estimate(cps_trim), estimate(psid_trim))

rownames(df) <- c("exp_df","cps_untrim","psid_untrim","cps_trim","psid_trim")

# Print data frame
df
```

# AI Disclosure

I used ChatGPT to aid with debugging/checking code, R syntax and function tips, explanation of documentation, and code examples for how to use R packages such as ggplot2, etc. For some examples, when I didn't understand an error message, I would ask about the error in reference to the problematic code found through the traceback. I asked ChatGPT for suggestions on functions and packages to use for a given task, such as to create a balance plot.
